Impact ionization processes in a photodriven Mott insulator: influence of phononic dissipation

### 2022-11-03 resub_PRB/letters/reply_to_referees_jan.txt

Dear Dr. Kancharla,

Thank you very much for your e-mail from October 24th with the reply of the Referees on our paper. The first Referee recommends publication without hesitation. The second Referee believes that the paper has to be published in Physical Review B, after discussing the points she/he raised.

@@

1. As the authors pointed out the electric field amplitude considered
in this paper is several orders of magnitude larger than that of the
sunlight, therefore, strictly speaking the results presented in the
present paper are more applicable to intense laser-light
photoexcitations

2. The authors have made an effort to extrapolate in the regime of
smaller electric field amplitude and smaller hybridization strength.
They note that in order to achieve the latter one would need to
several layers where photexcited carriers separated by an electric
field gradient would have more time to induce impact ionization before
escaping into the leads.

3. The authors plan in future investigation to address the previously
mentioned issue.

A1-A2-A3: We thank the Referee for her/his remarks and aprreciation of our article.

@@

4. I would like to suggest that, perhaps, the authors, in their future
investigations, could include the role of "bad" metallic contacts,
maybe represented by narrow-band leads or possibly with a small-width
insulating barrier between the leads and the material as abstracted by
the Hubbard-like model studied. If the insulating barrier is
microscopically small the carriers would still be able to tunnel, but
perhaps would remain longer in the region of the material which might
allow II to occur.

A4: Thank you for this suggestion, which is an interesting input for  future investigations.

@@

----------------------------------------------------
        Second Referee                              
----------------------------------------------------

************************************************************************
*** To highlight the changes in the main text we marked them in BLUE ***
************************************************************************

1. It is really important to discuss why DMFT approximation is
expected to be meaningful in quasi-2D case (1-layer Hubbard model
coupled to leads).

A1: As the Referee says, the system is not strictly 2D. There is a coupling in the third direction due to the hybridisation to the leads. Although these are noninteracting, they introduce a dissipation which suppresses 2D coherence and makes nonlocal correlations less relevant.

On the other hand, antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in prl 113,076405 (2014). These nonlocal effects are not taken into account in our paper and certain deserve future investigations.

@@

2. It seems that chosen temperature is pretty high. Please discuss why
optical phonons are neglected.

A2:

We thank the Referee for raising this point, giving us the opportunity for further clarification.

The value of the temperature of T=0.02 is not large as compared with the other characteristic energy scales of the system, e.g. the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12, as well as the bandwidth. In addition taking the energy scale of about 1eV, it roughly corresponds to  room temperature.  
In our simplified model we neglected optical phonons because they are less effective than acoustic ones in dissipating energy, as we mentioned in Sec. II

@@

As the Referee suggests, we inserted a footnote in Sec. IV, addressing this point explicitly.

3. It is naturally expected that phonons reduce the bandgap (here,
pseudogap), as in standard semiconductors, where the phonons give
10-100meV reduction of the gap and the effect increases with
temperature. Strictly speaking, to obtain the change of the
bandstructure due to phonons one needs to calculate the Fan and DW
terms of the, generally speaking, momentum-dependent electron
self-energy. In this sense, again, how important are momentum
dependencies of electron Sigma in 2D case?

A3: We thank the Referee for pointing out this issue, which  we address it below.

The importance of the momentum dependence of the electron self-energy in the 2D case depends on the level of sophistication one wants to achieve in considering acoustic phonons and therefore whether one wants quantitative results or qualitative/semi-quantitative results are sufficient. As explicitly stated in Sec. I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work."
Let us mentioned that  the Fan (alias  self-energy in the Migdal approximation, see Rev. Mod. Phys. 89, 015003 (2017)) has been included in our calculation,  albeit without momentum dependence. The static Debye-Waller term corresponds in our DMFT case to a shift in the chemical potential, which is zero in the present particle-hole symmetric case.

@@

4. It is not clear from Conclusions (at least for me) what stopped the
authors to consider more realistic weaker fields and hybridizations.

A4:

We did not consider weaker electric field amplitudes since DMFT only converges slowly for such a choice of parameters. We have already discussed this point in the footnote [47]. The same reasoning applies for smaller hybridization strength which slows down the convergence of the DMFT cycle considerably.

Prompted by the Referee's comment we moved the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.

### 2022-11-04 resub_PRB/letters/reply_to_referees_current.txt

----------------------------------------------------
        Second Referee                              
----------------------------------------------------

************************************************************************
*** To highlight the changes in the main text we marked them in BLUE ***
************************************************************************

1. It is really important to discuss why DMFT approximation is
expected to be meaningful in quasi-2D case (1-layer Hubbard model
coupled to leads).

A1: As the Referee says, the system considered here is not strictly 2D. There is a coupling in the third direction due to the hybridisation to the leads. Although these are noninteracting, they introduce a dissipation which suppresses 2D coherence and makes nonlocal correlations less relevant.

On the other hand, it is true that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in prl 113,076405 (2014). These nonlocal effects are not taken into account in our paper and certain deserve future investigations.

@@

As asked, we added in Sec. I a discussion on this point, with a reference to a comprehensive review of nonlocal correlations beyond DMFT [Rev. Mod. Phys. 90, 025003 (2018)].

2. It seems that chosen temperature is pretty high. Please discuss why
optical phonons are neglected.

A2: The value of the temperature of T=0.02 is not large as compared with the other characteristic energy scales of the system, e.g. the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12, as well as the bandwidth. In addition taking the energy scale of about 1eV, it roughly corresponds to  room temperature.  
In our simplified model we neglected optical phonons because they are less effective than acoustic ones in dissipating energy, as we mentioned in Sec. II

@@

As the Referee suggests, we inserted a footnote in Sec. IV, addressing this point explicitly.

3. It is naturally expected that phonons reduce the bandgap (here,
pseudogap), as in standard semiconductors, where the phonons give
10-100meV reduction of the gap and the effect increases with
temperature. Strictly speaking, to obtain the change of the
bandstructure due to phonons one needs to calculate the Fan and DW
terms of the, generally speaking, momentum-dependent electron
self-energy. In this sense, again, how important are momentum
dependencies of electron Sigma in 2D case?

A3: We thank the Referee for pointing out this issue, which  we now address  below and in the paper.

The importance of the momentum dependence of the electron self-energy in the 2D case depends on the level of sophistication one wants to achieve in considering acoustic phonons and therefore whether one wants quantitative results or qualitative/semi-quantitative results are sufficient. As explicitly stated in Sec. I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work." In this sense, we don't expect a momentum dependent Sigma would change the overall picture obtained in our work. We are not looking at a detailed band structure change.
We have included Fan terms (alias  Migdal terms, see Rev. Mod. Phys. 89, 015003 (2017)) in our calculation, although without vertex corrections and momentum dependence. Neglecting the DW term, as we do is consistent with neglecting phonon self-consistency and restricting to first order terms in the phonon displacement.

%EACOMM I would discuss this point in the conclusions as further things one could do.
We included a footnote in Sec. III.B addressing the momentum-dependence, together with a reference to the review mentioned above.

@@

4. It is not clear from Conclusions (at least for me) what stopped the
authors to consider more realistic weaker fields and hybridizations.

A4:

We did not consider weaker electric field amplitudes since DMFT only converges slowly for such a choice of parameters. We have already discussed this point in the footnote [47]. The same reasoning applies for smaller hybridization strength which slows down the convergence of the DMFT cycle considerably.

In connection with the Referee's comment we moved the footnote [47] into the main text in Sec. V and extending it to mention smaller hybridizations.

### 2022-11-04 resub_PRB/letters/reply_to_referees_current.txt

1. As the authors pointed out the electric field amplitude considered
in this paper is several orders of magnitude larger than that of the
sunlight, therefore, strictly speaking the results presented in the
present paper are more applicable to intense laser-light
photoexcitations

2. The authors have made an effort to extrapolate in the regime of
smaller electric field amplitude and smaller hybridization strength.
They note that in order to achieve the latter one would need to
several layers where photexcited carriers separated by an electric
field gradient would have more time to induce impact ionization before
escaping into the leads.

3. The authors plan in future investigation to address the previously
mentioned issue.

A1-A2-A3: We thank the Referee for her/his remarks and appreciation of our article.

@@

4. I would like to suggest that, perhaps, the authors, in their future
investigations, could include the role of "bad" metallic contacts,
maybe represented by narrow-band leads or possibly with a small-width
insulating barrier between the leads and the material as abstracted by
the Hubbard-like model studied. If the insulating barrier is
microscopically small the carriers would still be able to tunnel, but
perhaps would remain longer in the region of the material which might
allow II to occur.

A4: We thank the Referee for this suggestion, which is an interesting input for future investigations.

@@

----------------------------------------------------
        Second Referee                              
----------------------------------------------------

************************************************************************
*** To highlight the changes in the main text we marked them in BLUE ***
************************************************************************

1. It is really important to discuss why DMFT approximation is
expected to be meaningful in quasi-2D case (1-layer Hubbard model
coupled to leads).

A1: As the Referee says, the system considered here is not strictly 2D. There is a coupling in the third direction due to the hybridization to the leads. Although these are noninteracting, they introduce a dissipation which suppresses 2D-coherence and makes nonlocal correlations less relevant.

On the other hand, it is true that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers, as discussed in Phys. Rev. Lett. 113, 076405
(2014). These nonlocal effects are not taken into account in our paper and certainly deserve future investigations.

As asked, we added in Sec. I a discussion on this point, with a reference to the paper mentioned above and to a comprehensive review of nonlocal correlations beyond DMFT [Rev. Mod. Phys. 90, 025003 (2018)].

@@

2. It seems that chosen temperature is pretty high. Please discuss why
optical phonons are neglected.

A2: The value of the temperature of T=0.02 is not large as compared with the other characteristic energy scales of the system, e.g. the soft cutoff of the acoustic phonon frequency w_ph=0.1 and the Hubbard interaction U=12, as well as the Hubbard bands bandwidth. In addition, if one takes the energy scale of about 1eV or less, this would correspond to the room temperature or below. 
In our simplified model, we neglected optical phonons because they are less effective than acoustic ones in dissipating energy, as we mentioned in Sec. II.

@@

As the Referee suggests, we inserted a footnote in Sec. IV, addressing this point explicitly.

3. It is naturally expected that phonons reduce the bandgap (here,
pseudogap), as in standard semiconductors, where the phonons give
10-100meV reduction of the gap and the effect increases with
temperature. Strictly speaking, to obtain the change of the
bandstructure due to phonons one needs to calculate the Fan and DW
terms of the, generally speaking, momentum-dependent electron
self-energy. In this sense, again, how important are momentum
dependencies of electron Sigma in 2D case?

A3: We thank the Referee for pointing out this issue, which  we now address  below and in the paper.

The importance of the momentum dependence of the electron self-energy in the 2D case depends on the level of sophistication one wants to achieve in considering acoustic phonons and therefore whether one wants quantitative results or qualitative/semi-quantitative results are sufficient. As explicitly stated in Sec. I, "...our analysis can only provide qualitative results, while quantitative comparisons with experimental systems require a more realistic setup and are beyond the scope of this work." In this sense, we don't expect that a momentum-dependent Sigma would change the overall picture obtained in our work. In fact, we are not looking at a detailed band structure change.
We have included the Fan term (alias  Migdal term, see Rev. Mod. Phys. 89, 015003 (2017)) in our calculation, although without vertex corrections and momentum dependence. Neglecting the DW term, as we do, is consistent with neglecting phonon self-consistency and restricting to first-order terms in the phonon displacement.

We included a discussion in Sec. V addressing this issue, together with a reference to the review mentioned above.

@@

4. It is not clear from Conclusions (at least for me) what stopped the
authors to consider more realistic weaker fields and hybridizations.

A4:

We did not consider weaker electric field amplitudes since DMFT only converges slowly for such a choice of parameters. We have already discussed this point in the footnote [47]. This holds also for smaller hybridization strengths which slow down the convergence of the DMFT cycle considerably.

In connection with the Referee's comment we moved the footnote [47] into the main text in Sec. V and we extended it to mention smaller hybridizations.

### 2022-11-04 resub_PRB/Paper1.tex
Version modified following Enrico's suggestions

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The leads have themselves a wide band, as expected for good conductors, which is effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy. We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT)\resub{, which has been shown to give meaningful results in similar setups (see, e.g.~\cite{so.do.18}). Since we are not interested in capturing long-ranged collective excitations, non-local correlations~\cite{ro.ha.18} are not taken into account.}

\begin{figure}[b] 
\includegraphics[width=0.9\linewidth]{Fig1.pdf}
\caption{(Color online) Schematic representation of the setup. A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black). The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce broadenings $\Gamma_{\text{l}/\text{r}}$.}
\label{fig:setup}
\end{figure}

@@

The electron SE $\kel{\mat{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e. $\kel{\mat{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}. In the same spirit, the e-ph SE is included locally as $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$~\footnote{\resub{As stated in Sec.~\ref{sec:intro}, our analysis provides only qualitative results. A more accurate treatment that aims to provide quantitative predictions, should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$. We refer to the review~\cite{gius.17} which discusses the effects of phonons on the electronic bandstructure and the modelling thereof.}}\vphantom{\cite{gius.17}}. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form      
% 
\begin{equation}\label{eq:backbone_e-ph_SE}
\Sigma_{\text{e-ph}}(z,z^{\prime}) = \ii g^{2} G(z,z^{\prime}) D_{\text{ph}}(z,z^{\prime}).
\end{equation}
% 
The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
%
\begin{align}\label{eq:Ph_Prop_time}
\begin{split} 
D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -\ii \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
D^{>}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left[ 1 + b(\omega) \right] \\
D^{<}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
\end{split}, 
\end{align}
%
where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$. We consider acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}. The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22}.

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is the smallest energy scale as compared to the other parameters of the system, e.g. $\omega_{\text{ph}}$ and $U$. For this reason, we can neglect optical phonons in our qualitative treatment.}}. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of the leads' spectra are formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving. Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$. All simulations are carried out with the dimensionless factor $\alpha\equiv t_{\text{resc}}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{\text{resc}}=1$, we define for consistency $\alpha$ as in the main text.}. Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

Experimentally, the electric field amplitude considered in this paper is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems. \resub{We did not consider smaller electric field amplitudes due to the slow F-DMFT convergence for such a choice of parameters. This also occurs for smaller hybridization strengths.}

On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction to smaller electric field amplitudes, for which a smaller hybridization would be necessary in order to sustain II. In a more realistic setup modelling oxide heterostructures~\cite{as.bl.13,pe.be.19}, a regime of effectively small hybridization would be achieved by considering several layers in which photoexcited carriers, separated by an electric field gradient, have more time to induce II processes before escaping into the leads. To address the occurrence of II in such a setup, further extensions such as considering multiple orbitals and impurity scattering should be taken into account. These would be interesting for future studies.

@@

We thank A. Picano for fruitful discussions. This work was supported by the Austrian Science Fund (FWF) within Project P 33165-N, as well as NaWi Graz. The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.

>>>>

For this goal we consider the simplified model shown in Fig.~\ref{fig:setup}, consisting of a Hubbard layer located between two leads. The leads have themselves a wide band, as expected for good conductors, which is effectively narrowed due to the weak coupling to intermediate layers which we take as simplified models for the contacts. Electrons on the Hubbard layer interact locally with acoustic phonons. An external periodic electric field induces a Floquet steady state with a current flowing from the lead with the lower to the lead with the higher chemical potential, thus transferring its energy. We address this periodic problem via nonequilibrium Floquet dynamical mean-field theory (F-DMFT)\resub{, which has been shown to give meaningful results in quasi-2D setups (see, e.g.~\cite{so.do.18}) as the one considered, in which the coupling in a third direction, due to the hybridization to the leads, introduces a dissipation which suppresses 2D-coherence and makes nonlocal correlations less relevant. However, it has been shown that antiferromagnetic (even short-range) correlations may play an important role in the spreading of photoexcited carriers~\cite{ec.we.14}. In this paper, we explicitly don't take into account these nonlocal effects~\cite{ro.ha.18}.}

\begin{figure}[b] 
\includegraphics[width=0.75\linewidth]{Fig1.pdf}
\caption{(Color online) Schematic representation of the setup. A central, correlated layer with local Hubbard interaction $U$ and e-ph coupling $g$ (green) is sandwiched between two non-interacting layers (red) via the hybridization $v$ (black). The latter are in turn coupled to wide-band fermion reservoirs (blue) with different chemical potentials $\mu_{\text{l}/\text{r}}$, which introduce broadenings $\Gamma_{\text{l}/\text{r}}$.}
\label{fig:setup}
\end{figure}

@@

The electron SE $\kel{\mat{\Sigma}}$ is obtained from F-DMFT and therefore, in this approximation, independent of the crystal momentum, i.e. $\kel{\mat{\Sigma}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}(\omega)$. Further details are given in Sec.~\ref{sec:FDMFT_implementation}. In the same spirit, the e-ph SE is included locally as $\kel{\mat{\Sigma}}_{\text{e-ph}}(\omega;\epsilon,\overline{\epsilon}) \simeq \kel{\mat{\Sigma}}_{\text{e-ph}}(\omega)$. In terms of the Keldysh contour time arguments $z$ and $z^\prime$, it has the form      
% 
\begin{equation}\label{eq:backbone_e-ph_SE}
\Sigma_{\text{e-ph}}(z,z^{\prime}) = \ii g^{2} G(z,z^{\prime}) D_{\text{ph}}(z,z^{\prime}).
\end{equation}
% 
The Keldysh components of the non-interacting phonon GF $\kel{D}_{\text{ph}}(t,t^{\prime})$ are given by~\cite{ao.ts.14}
%
\begin{align}\label{eq:Ph_Prop_time}
\begin{split} 
D^{\text{R}}_{\text{ph}}(t,t^{\prime}) & = -\ii \theta(t-t^{\prime}) \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega), \\
D^{>}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \left[ 1 + b(\omega) \right] \\
D^{<}_{\text{ph}}(t,t^{\prime}) & = -\ii \int \dd\omega \ \ee^{-\ii\omega\left(t-t^{\prime}\right)} A_{\text{ph}}(\omega) \ b(\omega), \\
\end{split}, 
\end{align}
%
where $b(\omega)=1/(\ee^{\beta\omega}-1)$ is the Bose-Einstein distribution function at inverse temperature $\beta$. We consider acoustic phonons, with spectral function $A_{\text{ph}}(\omega) = (\omega/\omega^{2}_{\text{ph}}) \ee^{-| \omega|/\omega_{\text{ph}}}$,  $\omega_{\text{ph}}$ being a soft cutoff frequency~\cite{pi.li.21}. The retarded and Keldysh components of the e-ph SE are easily extracted from  Eq.~\eqref{eq:backbone_e-ph_SE} and can be found in Ref.~\cite{ma.ga.22}.

@@

In order to study II in a Mott insulating layer, we adjust the bands to achieve the energy scheme shown in Fig.~\ref{fig:energy_setup}(a). We follow Ref.~\cite{so.do.18} and take $U=12$ and unless stated otherwise $E_0=2$. The fermion leads and the acoustic phonons have temperature $T=0.02$~\footnote{\resub{The value chosen for the temperature is small as compared with the other characteristic energy scales of the system, e.g. $\omega_{\text{ph}}$, $U$ and $W_{\text{b}}$.}}. We consider a particle-hole symmetric system with $\Gamma_{\text{l}}=\Gamma_{\text{r}}=0.37$, $t_{\text{l}}=t_{\text{r}}=1.7$, $\varepsilon_{\text{l}/\text{r}}=\mp 6$ and $v_{\text{l}}=v_{\text{r}}=v$. The parameters $t_{\text{l/r}}$, $\varepsilon_{\text{l/r}}$, and  $\Gamma_{\text{l/r}}$ are chosen such that the leads' DOS approximately overlaps with the Hubbard bands, i.e. they exhibit a \textquoteleft bandwidth\textquoteright~\footnote{Notice that the support of the leads' spectra are formally infinite. $W_{\text{b}}$ is the value at which the spectrum gets  suppressed.} $W_{\text{b}}\approx 8$ and are centered at the same position. The chemical potentials are set to $\mu_{\text{l}/\text{r}} =\mp 1$, so that a current from left to right is produced by taking energy from the driving. Due to the hybridization with the leads, the local DOS of the Hubbard layer only features a pseudogap
 $\Delta_{\text{pg}} \approx 4$. All simulations are carried out with the dimensionless factor $\alpha\equiv t_{\text{resc}}E_0/\Omega^{2}<0.5$ for which the FDSA is justified~\footnote{In Ref.~\cite{so.do.18} the factor is defined as $\alpha=t_{c}E_0/\Omega^{2}$ and $t_{\text{c}}=1$. Setting $t_{\text{resc}}=1$, we define for consistency $\alpha$ as in the main text.}. Whenever the electron-phonon interaction is included, we take $g=0.8$ and unless stated otherwise $\omega_{\text{ph}}=0.1$.

@@

Experimentally, the electric field amplitude considered in this paper is several orders of magnitude larger than that of the sunlight, therefore our results are more relevant for photoexcitations produced by intense laser pulses (see also the discussion in~\cite{mu.we.18}) rather than for true photovoltaic systems. \resub{We did not consider smaller electric field amplitudes due to the slow F-DMFT convergence for such a choice of parameters. This also occurs for weaker hybridization strengths.}

On the other hand, one may try to qualitatively extrapolate the discussion at the end of Sec.~\ref{sec:E0_2_only_electrons} in the other direction to smaller electric field amplitudes, for which a smaller hybridization would be necessary in order to sustain II. In a more realistic setup modelling oxide heterostructures~\cite{as.bl.13,pe.be.19}, a regime of effectively small hybridization would be achieved by considering several layers in which photoexcited carriers, separated by an electric field gradient, have more time to induce II processes before escaping into the leads. To address the occurrence of II in such a setup, further extensions such as considering multiple orbitals and impurity scattering should be taken into account. \resub{Finally, a more realistic description of the effects of the electron-phonon interaction on electronic band structure should take into account the crystal momentum dependence of $\kel{\mat{\Sigma}}_{\text{e-ph}}$~\cite{gius.17}.} These would be interesting for future studies.

@@

We thank A. Picano and C. Heil for fruitful discussions. This work was supported by the Austrian Science Fund (Grant No. P 33165-N) and by NaWi Graz. The computational results presented have been obtained using the Vienna Scientific Cluster (VSC) and the D-Cluster Graz.
